---
title: "My Fitbit overview"
output: html_document
---

*How to run this doc*

1. Install the [FitbitAnalysis](https://github.com/kaybrodersen/FitbitAnalysis)
   package.
2. Update `kInputPath` below to point to your downloaded Fitbit archive.
3. Open this doc in RStudio and run 'Knit' or
   `knitr::knit("rmd/my_overview.Rmd")`. To check the location of the doc, try:
   `system.file("rmd", "my_overview.Rmd", package = "FitbitAnalysis")`.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, echo=FALSE}
options(warn = -1)
```

## Input data

```{r constants}
kInputPath <- "/path/to/MyFitbitData/FirstnameLastname/"
```

```{r}
library(FitbitAnalysis)
data <- suppressMessages(LoadFitbitData(kInputPath))
head(data)
```

## Daily metrics

Raw daily values of all metrics in the data, including a weekly moving average.

```{r}
PlotMetrics(data)
```

## Weekly sums

This plot shows weekly data, which may show long-term trends more easily than
daily values.

```{r}
PlotWeeklyMetrics(data)
```

## Day-of-week averages

This plot highlights day-of-week patterns across all metrics.

```{r}
PlotWeekdayMetrics(data)
```

## Time at rest

This plot shows the distribution of beginning and end of sleep times.

```{r}
PlotTimeAtRest(data)
```

## Minutes awake vs. start hour

This plot regresses minutes awake on the start hour of every night to highlight
how the two are related.

```{r}
PlotMinutesAwakeVsStartHour(data)
```
